Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 nge.tex
Negative spaces fixing

As seen in \S\ref{sec:panda_deployment}, PanDA Broker was  deployed on the DTNs
as Titan's worker nodes lack connectivity to the wide area network The lack of
pilot capabilities impacts both the efficiency and the flexibility of PanDA's
execution process. Pilots could improve efficiency by increasing throughput and
enabling greater backfill utilization. Further, pilots makes it easier to
support heterogeneous workloads.

@@

Multiple generations would also relax two assumptions of the current execution
model: knowing the number of simulations before submitting the MPI script, and
having a fixed number of events per simulation (100 at the moment). Pilots would
enable the scheduling of simulations independently from whether they were
available at the moment of submitting the pilot. Further, simulations with a
varying number of events could be scheduled on a pilot, depending on the amount
of remaining walltime and the distribution of execution time per event, as shown
in \S\ref{ssec:panda_titan}, Fig.~\ref{fig:100event- distrib}. These
capabilities would increase the efficiency of the PanDA Broker when there is a
large difference between the number of cores and walltime.

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{figures/rp_architecture_compact_atlaswms_paper.pdf}
  \caption{NGE Architecture: The PilotManager and  UnitManager reside on a Titan
  DTN while the Agent is executed on its worker nodes. Color coding: gray for
  entities external to NGE, white for APIs, purple for NGE's modules, green for
  pilots, yellow for module's components.}
\label{fig:arch-overview}
\end{figure}

>>>>

As seen in \S\ref{ssec:panda_titan}, PanDA Broker was  deployed on the DTNs
as Titan's worker nodes lack connectivity to the wide area network The lack of
pilot capabilities impacts both the efficiency and the flexibility of PanDA's
execution process. Pilots could improve efficiency by increasing throughput and
enabling greater backfill utilization. Further, pilots makes it easier to
support heterogeneous workloads.

@@

Multiple generations would also relax two assumptions of the current execution
model: knowing the number of simulations before submitting the MPI script, and
having a fixed number of events per simulation (100 at the moment). Pilots would
enable the scheduling of simulations independently from whether they were
available at the moment of submitting the pilot. Further, simulations with a
varying number of events could be scheduled on a pilot, depending on the amount
of remaining walltime and the distribution of execution time per event, as shown
in \S\ref{ssec:panda_titan}, Fig.~\ref{fig:comparison-8-16cores}. These
capabilities would increase the efficiency of the PanDA Broker when there is a
large difference between the number of cores and walltime.

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{figures/rp_architecture_compact_atlaswms_paper.pdf}
   \vspace{-0.3in}
  \caption{NGE Architecture: The PilotManager and  UnitManager reside on a Titan
  DTN while the Agent is executed on its worker nodes. Color coding: gray for
  entities external to NGE, white for APIs, purple for NGE's modules, green for
  pilots, yellow for module's components.}
\label{fig:arch-overview}
\end{figure}
